High Performance Silicon Grisms for 1.2-8.0 {\LARGE$\bm{\mu}$}m: Detailed Results from the JWST-NIRCam Devices

### 2015-03-25 chSPIE_2010_JWST/mgs_spie_2010_v1_5.tex
append the directory path to the figure name, and clean the references to get the SPIE 2010 document to compile

We have delivered a set of silicon grisms for use as dispersive elements in the long wavelength channel of the near-infrared camera (NIRCam)\cite{Horner04, Greene10} on the James Webb Space Telescope (JWST)\cite{Sabelhaus04}.  The primary function of these grisms is to produce spectra for dispersed fringe sensing which will permit elimination of piston errors as the telescope is aligned to its design figure\cite{Shi08}. The NIRCam-based dispersive fringe sensing system, by virtue of its long operating wavelength, has a significantly larger capture range than the equivalent optical system.  The grisms also offer the possibility of astronomical observations that can make use of NIRCam's ability to conduct slitless spectroscopy at 3-5 $\mu$m over a large field.  One important application is infrared spectroscopy of transiting planets where the absence of a slit eliminates the problem of time-variable slit losses\cite{Greene07}.  Science operations in the NIRCam grism mode will be supported by the JWST data planning and data taking software.

@@

   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=9cm]{A6K_scale.png}
   \end{tabular}
   \end{center}
   \caption[JWST grism [pictures] 
   { \label{fig:im1} 
Photograph of flight grism ``A6K" for JWST-NIRCam.  The outer diameter is 48 mm and the part has an optically usable diameter of 42 mm.  The forward-facing surface has grooves with a period of 15.36 $\mu$m.  The opposite surface has been polished optically flat.  The flats along the perimeter serve as mounting and orientation surfaces}
   \end{figure}

@@

   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=7cm]{A7I_entrance_uncoat.png}
   \end{tabular}
   \end{center}
   \caption[A7-I interferogram] {\label{fig:im2}  Interferogram of the polished entrance surface of JWST trial grism ``A7-I".  The interferogram was taken prior to the application of an antireflection coating. }
   \end{figure}

\subsection{Groove Geometry}
We form the grooves in the monolithic substrates from which we fabricate the grisms by taking advantage of the significantly different rates at which certain chemicals etch through the different planes in crystalline structure\cite{Marsh07, Tsang1975}.  In our process a solution of KOH etches approximately 60 times faster across the 100 plane than across the 111 plane and a suitably oriented mask of stripes will form triangular grooves at the intersection of 111 planes.  The intersecting planes form an angle of $71\,^{\circ}{\rm}$.  For blaze angles greater than $8\,^{\circ}{\rm}$, this acute angle will result in shadowing of one groove by another in transmission with the amount of shadowing a function of the blaze angle (see Figure 6 of Mar et al. (2006)\cite{Mar06}).  For small prism opening angles, it is not the acute groove vertex but rather the small dams along the grating surface that lead to groove filling factors less than one.  We need the dams to serve as etch stops between the grooves.  For the JWST gratings, the grating constant was 15.36 $\mu$m and the final dam width was about 1.5 $\mu$m.  At the $6.16 \,^{\circ}{\rm}$ opening angle of the JWST prisms, the dams are responsible for the filling factor loss.  The geometric blockage whether by the dams or by the lip of the neighboring acute groove leads to loss in two ways:  direct blockage of the light and, via Babinet's principle, diffraction of an equal amount of light into unwanted orders.  For the geometric blockage of $\sim10\%$ in the JWST grisms, the maximum theoretical transmission is then 0.81.

@@

%Figure 3
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=9cm]{A6I_transmission_nt2}
   \end{tabular}
   \end{center}
   \caption[JWST grism transmission] {\label{fig:im3}  Measurement of throughput as a function of wavelength for JWST flight part ``A6-I".  The combination of the geometric blockage by the groove dams and the Fresnel losses results in a theoretical maximum efficiency of $\sim 0.41$ on the blaze.  The plot shows the power in the fifth order and in adjacent orders.} 
   \end{figure}

@@

   %Figure 4
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=10cm]{ARcoat_trans_siww}
   \end{tabular}
   \end{center}
   \caption[Transmission of single side AR coated silicon wafer witness] {\label{fig:im4}  IR transmission of an optically flat thin silicon wafer witness that was AR coated on a single side.  The wafer does not have grooves on it, and therefore does not have geometric losses.  Since the uncoated air-Si interface suffers 30\% Fresnel loss, the AR coated interface must exhibit close to 100\% transmission between 2 and 5 $\mu$m.  The AR coating is ineffective shortward of 2 $\mu$m, and Si does not transmit short of 1.15$\mu$m.  Figure courtesy of II-VI Inc.} 
   \end{figure}

@@

%Figure 5: a) Transmission of uncoated trial part
                 %b) Transmission of coated trial part
   \begin{figure}
   \begin{minipage}[b]{0.5\linewidth} % A minipage that covers half the page
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{A7I_uncoated_trans.pdf}
   \end{tabular}
   \end{minipage}
   \hspace{0.01cm} % To get a little bit of space between the figures
\begin{minipage}[b]{0.5\linewidth}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{A7I_coated_2.pdf}
   \end{tabular}
   \end{minipage}
   \caption[JWST grism transmission] {\label{fig:im5}  Transmission of trial part A7-I.  The interferograms were taken with the surfaces (left) uncoated and (right) coated on both entrance and grating surfaces.  The ineffectiveness of the AR coating shortward of 2.0 $\mu$m (cf. Figure 4) stifled a direct comparison of transmission at the same wavelengths before and after coating.  The poor transmission below 2.0 $\mu$m is apparent in the right panel, since the $4^{th}$ order curve is suppressed before it reaches its blaze peak near 1.8 $\mu$m.  A similar measurement at 3.1-4.0 $\mu$m shows 75\% peak efficiency for the double-side coated grism.}
   \end{figure}

@@

%Figure 6: a) Interferometry of uncoated trial part 31mm
                 %b) Interferometry of coated trial part 31mm
   \begin{figure}
   \begin{minipage}[b]{0.5\linewidth} % A minipage that covers half the page
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{A7I_interf_31mm_grat_uncoat.png}
   \end{tabular}
   \end{center}
   \end{minipage}
   \hspace{0.0001cm} % To get a little bit of space between the figures
\begin{minipage}[b]{0.5\linewidth}
\begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{A7I_post_coat.png}
   \end{tabular}
   \end{center}
   \end{minipage}
   \caption[Trial part groove interferogram] {\label{fig:im6}  Optical interferograms at 633nm of the central 31 mm of the grooved surfaces of the trial part, A7-I.  The left figure shows the grooved surface before AR coating.  On the right is the interferogram of the grating surface after AR coating.  The RMS and peak to valley wavefront errors are printed at the bottom of the figures- \em{before}\em: PV- 0.0308, RMS- 0.0061 waves; \em{after}\em: PV- 0.0557, RMS- 0.0120 waves.}
   \end{figure}

>>>>

We have delivered a set of silicon grisms for use as dispersive elements in the long wavelength channel of the near-infrared camera (NIRCam)\cite{Horner04,Greene10} on the James Webb Space Telescope (JWST)\cite{Sabelhaus04}.  The primary function of these grisms is to produce spectra for dispersed fringe sensing which will permit elimination of piston errors as the telescope is aligned to its design figure\cite{Shi08}. The NIRCam-based dispersive fringe sensing system, by virtue of its long operating wavelength, has a significantly larger capture range than the equivalent optical system.  The grisms also offer the possibility of astronomical observations that can make use of NIRCam's ability to conduct slitless spectroscopy at 3-5 $\mu$m over a large field.  One important application is infrared spectroscopy of transiting planets where the absence of a slit eliminates the problem of time-variable slit losses\cite{Greene07}.  Science operations in the NIRCam grism mode will be supported by the JWST data planning and data taking software.

@@

   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=9cm]{chSPIE_2010_JWST/figs/A6K_scale.png}
   \end{tabular}
   \end{center}
   \caption[JWST grism [pictures] 
   { \label{fig:im1} 
Photograph of flight grism ``A6K" for JWST-NIRCam.  The outer diameter is 48 mm and the part has an optically usable diameter of 42 mm.  The forward-facing surface has grooves with a period of 15.36 $\mu$m.  The opposite surface has been polished optically flat.  The flats along the perimeter serve as mounting and orientation surfaces}
   \end{figure}

@@

   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=7cm]{chSPIE_2010_JWST/figs/A7I_entrance_uncoat.png}
   \end{tabular}
   \end{center}
   \caption[A7-I interferogram] {\label{fig:im2}  Interferogram of the polished entrance surface of JWST trial grism ``A7-I".  The interferogram was taken prior to the application of an antireflection coating. }
   \end{figure}

\subsection{Groove Geometry}
We form the grooves in the monolithic substrates from which we fabricate the grisms by taking advantage of the significantly different rates at which certain chemicals etch through the different planes in crystalline structure\cite{Marsh07,Tsang1975}.  In our process a solution of KOH etches approximately 60 times faster across the 100 plane than across the 111 plane and a suitably oriented mask of stripes will form triangular grooves at the intersection of 111 planes.  The intersecting planes form an angle of $71\,^{\circ}{\rm}$.  For blaze angles greater than $8\,^{\circ}{\rm}$, this acute angle will result in shadowing of one groove by another in transmission with the amount of shadowing a function of the blaze angle (see Figure 6 of Mar et al. (2006)\cite{Mar06}).  For small prism opening angles, it is not the acute groove vertex but rather the small dams along the grating surface that lead to groove filling factors less than one.  We need the dams to serve as etch stops between the grooves.  For the JWST gratings, the grating constant was 15.36 $\mu$m and the final dam width was about 1.5 $\mu$m.  At the $6.16 \,^{\circ}{\rm}$ opening angle of the JWST prisms, the dams are responsible for the filling factor loss.  The geometric blockage whether by the dams or by the lip of the neighboring acute groove leads to loss in two ways:  direct blockage of the light and, via Babinet's principle, diffraction of an equal amount of light into unwanted orders.  For the geometric blockage of $\sim10\%$ in the JWST grisms, the maximum theoretical transmission is then 0.81.

@@

%Figure 3
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=9cm]{chSPIE_2010_JWST/figs/A6I_transmission_nt2}
   \end{tabular}
   \end{center}
   \caption[JWST grism transmission] {\label{fig:im3}  Measurement of throughput as a function of wavelength for JWST flight part ``A6-I".  The combination of the geometric blockage by the groove dams and the Fresnel losses results in a theoretical maximum efficiency of $\sim 0.41$ on the blaze.  The plot shows the power in the fifth order and in adjacent orders.} 
   \end{figure}

@@

   %Figure 4
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=10cm]{chSPIE_2010_JWST/figs/ARcoat_trans_siww}
   \end{tabular}
   \end{center}
   \caption[Transmission of single side AR coated silicon wafer witness] {\label{fig:im4}  IR transmission of an optically flat thin silicon wafer witness that was AR coated on a single side.  The wafer does not have grooves on it, and therefore does not have geometric losses.  Since the uncoated air-Si interface suffers 30\% Fresnel loss, the AR coated interface must exhibit close to 100\% transmission between 2 and 5 $\mu$m.  The AR coating is ineffective shortward of 2 $\mu$m, and Si does not transmit short of 1.15$\mu$m.  Figure courtesy of II-VI Inc.} 
   \end{figure}

@@

%Figure 5: a) Transmission of uncoated trial part
                 %b) Transmission of coated trial part
   \begin{figure}
   \begin{minipage}[b]{0.5\linewidth} % A minipage that covers half the page
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{chSPIE_2010_JWST/figs/A7I_uncoated_trans.pdf}
   \end{tabular}
   \end{minipage}
   \hspace{0.01cm} % To get a little bit of space between the figures
\begin{minipage}[b]{0.5\linewidth}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{chSPIE_2010_JWST/figs/A7I_coated_2.pdf}
   \end{tabular}
   \end{minipage}
   \caption[JWST grism transmission] {\label{fig:im5}  Transmission of trial part A7-I.  The interferograms were taken with the surfaces (left) uncoated and (right) coated on both entrance and grating surfaces.  The ineffectiveness of the AR coating shortward of 2.0 $\mu$m (cf. Figure 4) stifled a direct comparison of transmission at the same wavelengths before and after coating.  The poor transmission below 2.0 $\mu$m is apparent in the right panel, since the $4^{th}$ order curve is suppressed before it reaches its blaze peak near 1.8 $\mu$m.  A similar measurement at 3.1-4.0 $\mu$m shows 75\% peak efficiency for the double-side coated grism.}
   \end{figure}

@@

%Figure 6: a) Interferometry of uncoated trial part 31mm
                 %b) Interferometry of coated trial part 31mm
   \begin{figure}
   \begin{minipage}[b]{0.5\linewidth} % A minipage that covers half the page
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{chSPIE_2010_JWST/figs/A7I_interf_31mm_grat_uncoat.png}
   \end{tabular}
   \end{center}
   \end{minipage}
   \hspace{0.0001cm} % To get a little bit of space between the figures
\begin{minipage}[b]{0.5\linewidth}
\begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{chSPIE_2010_JWST/figs/A7I_post_coat.png}
   \end{tabular}
   \end{center}
   \end{minipage}
   \caption[Trial part groove interferogram] {\label{fig:im6}  Optical interferograms at 633nm of the central 31 mm of the grooved surfaces of the trial part, A7-I.  The left figure shows the grooved surface before AR coating.  On the right is the interferogram of the grating surface after AR coating.  The RMS and peak to valley wavefront errors are printed at the bottom of the figures- \em{before}\em: PV- 0.0308, RMS- 0.0061 waves; \em{after}\em: PV- 0.0557, RMS- 0.0120 waves.}
   \end{figure}
